%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Intermediate Software Engineer} % Job title
    {Invisipay Inc.} % Organization
    {Halifax, CA} % Location
    {Jun. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Heavily contributed to computer vision development, especially on tracking side, for cashier-less checkout solutions, suggested integrating RFID with AI-based vision systems, improving accuracy by 35-50\%}
        \item {Architected edge-to-cloud systems using NVIDIA Jetson platforms, DeepStream SDK, and containerized tools, enabling scalable real-time processing across multiple retail deployments.}
        \item {Managed and mentored a team of 2 developers, delegating tasks, reviewing code, and ensuring timely project delivery.}
        \item {Designed network stuctures using the service topology to integrate different parts of the business applications.}
        \item {Developed backend business logic using Google Cloud tools to support analytics, real-time processing, and scalable operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Software Engineer} % Job title
    {Invisipay Inc.} % Organization
    {Halifax, CA} % Location
    {Sep. 2024 - Jun. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained the company website using modern JavaScript frameworks, ensuring great online presence and user experience.}
        \item {Created a cross-platform mobile application using Flutter, enabling clients to interact with the cashier-less checkout system in real time.}
        \item {Configured and maintained NVIDIA Jetson-based edge computing devices, integrating computer vision and AI models for real-time retail operations.}
        \item {Collaborated on cross-functional projects involving AI, and computer vision to enhance automated checkout solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Integration Developer} % Job title
    {Contractor} % Organization
    {Halifax, CA} % Location
    {Oct. 2023 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led web system projects, modernized legacy technologies, and developed full-stack web applications using popular web frameworks such as Django, Laravel and Next.js.}
        \item {Implemented and configured IT systems, including setting up cloud servers, managing databases, integrating with existing systems, and configuring CI/CD pipelines using AWS services.}
        \item {Diagnosed and resolved issues related to software applications, hardware, and network systems.}
        \item {Documented technical specifications, implemented Google Analytics and Mixpanel for business tracking, ensuring cost-effective solutions and client satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
